The Death of Distance: Mobile Internet and Political Trust in Africa \\ \vspace{0.75cm} \underline{Tables}

### 2025-02-24 tables/v_1/tables.tex
import folders

@@

\usepackage{hyperref}
\hypersetup{
        colorlinks=true,
        breaklinks,
        allcolors=[RGB]{128,0,0}
}

@@

\usepackage{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{url}
\usepackage{dcolumn}
\usepackage{ctable}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{seqsplit}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{soul}
\usepackage{float}
%\usepackage[multiple]{footmisc}
%\usepackage{longtable}
\usepackage{adjustbox}
\usepackage{rotating}

\usepackage{bbding} % checkmark symbol
\usepackage{comment} % checkmark symbol

@@

%Bibliography
\usepackage{natbib}
%\usepackage[autostyle]{csquotes}
%\usepackage[backend=bibtex, style=authoryear, natbib=true]{biblatex}
%\addbibresource{CCH.bib}

%%For Hypotheses and Subhypotheses
%\usepackage{ntheorem}
\newtheorem{hyp}{Hypothesis}
\makeatletter
\newcounter{subhyp}
\let\savedc@hyp\c@hyp
\newenvironment{subhyp}
 {%
  \setcounter{subhyp}{0}%
  \stepcounter{hyp}%
  \edef\saved@hyp{\thehyp}% Save the current value of hyp
  \let\c@hyp\c@subhyp     % Now hyp is subhyp
  \renewcommand{\thehyp}{\saved@hyp\alph{hyp}}%
 }
 {}
\newcommand{\normhyp}{%
  \let\c@hyp\savedc@hyp % revert to the old one
  \renewcommand\thehyp{\arabic{hyp}}%
}
\makeatother
%%%

@@

%Expectation opperator
\newcommand{\Expect}{{\rm I\kern-.3em E}}

@@

@@

\title{Internet and Nation Building in Africa\\  \vspace{0.75cm} \underline{Preliminary and incomplete }}

@@

\author{
\textbf{Illan Barriola} \\ CRED -- Paris II \\
\and \textbf{R\'{e}dha Chaba}\\ LEMMA -- Paris II \\
}

@@

\begin{table}[H]
    \sffamily
    \caption{{Effect of distance from the capital on political trust}}
    \centering
    %\footnotesize
    \resizebox{12cm}{!}{
    \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
    \\
    \toprule
    \toprule
    &  \multicolumn{4}{c}{{OLS}}  \\
    \cmidrule(r){2-5}
    &  \multicolumn{4}{c}{{Political trust}}  \\
    \cmidrule(r){2-5}
    & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}\\
        \cmidrule(r){2-3}
        \cmidrule(r){4-5}
        & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
     \midrule

     Distance from the capital&       0.284***&       0.270***&       0.681***&       0.397* \\
     \medskip
     &      (0.04)   &      (0.03)   &      (0.16)   &      (0.21)  \\
     \midrule
     \smallskip
    Individual \& regional controls  & Yes & Yes & Yes & Yes  \\
    \smallskip
    Country controls & Yes& No& Yes& No\\
    \smallskip
    Round FE & Yes & No& Yes & No\\
    \smallskip
    Country X Round FE       & No & Yes& No & Yes\\
    \smallskip
    Ethnic homeland FE & No & No & Yes& Yes\\
    \smallskip
    Observations           & 98,235   &       98,235   &        4,189   &        4,189   \\
    Adjusted-R$^2$        &       0.158   &       0.197   &       0.159   &       0.189   \\

                          \bottomrule
    \multicolumn{5}{p{12.5cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 20-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959). Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses. The set of individual controls
    includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, radio news consumption, newspaper news consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
    \end{tabular}
    }
    \end{table}

    \begin{table}[H]
        \sffamily
        \caption{Effect of internet coverage on political trust by distance}
        \centering
        %\footnotesize
        \resizebox{17cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
        \\
        \toprule
        \toprule
        & \multicolumn{5}{c}{{Base sample}}\\
        \cmidrule(r){2-6}
        & \multicolumn{1}{c}{{OLS}} & \multicolumn{3}{c}{{First Stage}} & \multicolumn{1}{c}{{2SLS}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-5}
            \cmidrule(r){6-6}
            & \multicolumn{1}{c}{{Political trust}} & \multicolumn{1}{c}{{Internet coverage}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{Distance $\times$ Internet coverage}} & \multicolumn{1}{c}{{Political trust}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            \cmidrule(r){5-5}    
            \cmidrule(r){6-6}    
            & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{(3)}} & \multicolumn{1}{c}{{(4)}}\\

@@

    Distance from the capital &0.463***&&&& 1.361***\\      
    \smallskip
    &      (0.05)   &&&&     (0.49)   \\
    Internet coverage     &       0.029   &&&&       1.470**  \\
    \smallskip
    & (0.06)   &&&&      (0.64)    \\ 
    \smallskip
    Distance from the capital $\times$ Internet coverage&      -0.480***&&&               &       -2.295**\\
    \smallskip  &       (0.10)   &&&               &      (1.09) \\

   Lightning strikes && -0.002*** && -0.000  \\
    \smallskip&& (0.00) && (0.00) \\
    Distance from the capital city $\times$ Lightning strikes&& 0.000 && -0.001**\\
    \medskip&& (0.00) && (0.00)\\

         \midrule
        SW \emph{F} - Lightning strikes &-&-& 19.66&- &-&-\\
        \smallskip
        SW \emph{F} - Distance $\times$ Lightning strikes &-&-& 11.13 &-&-&-\\
        \smallskip
        Individual \& regional controls  & Yes & Yes &&  Yes & Yes\\
        \smallskip
        Country X Round FE       & Yes & Yes&- & Yes & Yes \\
        \smallskip
        Observations       &       98,235    &99,414 && 99,414&       98,235  \\
        Adjusted-R$^2$    &       0.198    &-&-&-&  \\
                              \bottomrule
        \multicolumn{6}{p{27cm}}{\footnotesize \emph{Notes}: % Set font size to 8pt with 10pt line spacing
        \emph{Notes}: Robust standard errors clustered at the region x round level. The set of individual controls
        includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
    \end{tabular}}
        \end{table}

        \begin{table}[H]
            \sffamily
            \caption{{Other outcomes}}
            \centering
            %\footnotesize
            \resizebox{18cm}{!}{
            \begin{tabular}{@{\extracolsep{5pt}} l c c}
            \\
            \toprule
            \toprule
            & \multicolumn{2}{c}{2SLS}\\
            \cmidrule(r){2-3}
            &\multicolumn{1}{c}{{Vote against ruling party}}&  \multicolumn{1}{c}{{Country performance}}  \\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            & \multicolumn{1}{c}{{Base sample}} & \multicolumn{1}{c}{{Base sample}}\\
                \cmidrule(r){2-2}
                \cmidrule(r){3-3}
                & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}\\
             \midrule

             Distance from the capital&   -1.306***&       1.560***\\
             \smallskip
             &      (0.40)   &      (0.52)   \\
             Internet coverage     &      -1.370***&       1.565**  \\
             \smallskip
             &      (0.47)   &      (0.62)   \\
             Distance from the capital $\times$ Internet coverage&       2.614***&      -3.065***\\
             \medskip
             &       (0.92)   &      (1.16)   \\
             \midrule
             \smallskip
            Individual \& regional controls  & Yes & Yes\\
            \smallskip
            Country X Round FE       & Yes& Yes\\
            \smallskip
            Observations      &       99,414   &       98,512  \\            \bottomrule
            \multicolumn{3}{p{18cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
            includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
            education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
            \end{tabular}
            }
            \end{table}

            \begin{table}[H]
              \sffamily
              \caption{{Media and institutions freedom}}
              \centering
              %\footnotesize
              \resizebox{16cm}{!}{
              \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
              \\
              \toprule
              \toprule
              & \multicolumn{4}{c}{2SLS: Political trust}\\
              \cmidrule(r){2-5}
              & \multicolumn{4}{c}{{Base sample}}\\
              \cmidrule(r){2-5}
              &\multicolumn{2}{c}{{Media}}&  \multicolumn{2}{c}{{Institutions}}\\
              \cmidrule(r){2-3}
                  \cmidrule(r){4-5}
                  & \multicolumn{1}{c}{{Free}} & \multicolumn{1}{c}{{Captured}}& \multicolumn{1}{c}{{Free}} & \multicolumn{1}{c}{{Captured}}\\
                  \cmidrule(r){2-2}
                  \cmidrule(r){3-3}
                  \cmidrule(r){4-4}
                  \cmidrule(r){5-5}
                  & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
               \midrule

               Distance from the capital&     -4.922   &       1.133*** &       0.078   &       2.151***\\
               \smallskip
               &     (11.77)   &      (0.41)  &      (0.83)   &      (0.77)\\
               Internet coverage        &      -3.475   &       1.220* &       0.112   &       2.964***\\
               \smallskip
               &     (10.01)   &      (0.68)  &      (1.37)   &      (1.06) \\
            Distance from the capital $\times$ Internet coverage&       9.210   &      -2.160* &       0.391   &      -4.202**\\
            \medskip
            &     (21.19)   &      (1.22) &      (1.59)   &      (1.90)\\

               \midrule
               \smallskip
              Individual \& regional controls  & Yes & Yes & Yes & Yes\\
              \smallskip
              Country X Round FE       & Yes& Yes & Yes& Yes\\
              \smallskip
              Observations          &       48,174   &       50,061 &       45,238   &       52,997 \\
              \bottomrule
              \multicolumn{5}{p{15cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
              includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
              education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
              \end{tabular}
              }
              \end{table}

              \begin{table}[H]
                \sffamily
                \caption{{Individual heterogeneity}}
                \centering
                %\footnotesize
                \resizebox{16cm}{!}{
                \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c c c}
                \\
                \toprule
                \toprule
                & \multicolumn{8}{c}{2SLS: Political trust}\\
                \cmidrule(r){2-9}
                & \multicolumn{8}{c}{{Base sample}}\\
                \cmidrule(r){2-9}
                &\multicolumn{2}{c}{{Education}}&  \multicolumn{2}{c}{{Urban/Rural}}&  \multicolumn{4}{c}{{Age}}\\
                \cmidrule(r){2-3}
                    \cmidrule(r){4-5}
                    \cmidrule(r){6-9}
                    & \multicolumn{1}{c}{{$<$ Secondary}} & \multicolumn{1}{c}{{$\geq$ Secondary}}& \multicolumn{1}{c}{{Urban}} & \multicolumn{1}{c}{{Rural}} & \multicolumn{1}{c}{{18-25}}& \multicolumn{1}{c}{{26-35}}& \multicolumn{1}{c}{{36-44}}& \multicolumn{1}{c}{{45+}}\\
                    \cmidrule(r){2-2}
                    \cmidrule(r){3-3}
                    \cmidrule(r){4-4}
                    \cmidrule(r){5-5}
                    \cmidrule(r){6-6}
                    \cmidrule(r){7-7}
                    \cmidrule(r){8-8}
                    \cmidrule(r){9-9}
                    & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}} &  \multicolumn{1}{c}{{(5)}} &  \multicolumn{1}{c}{{(6)}} &  \multicolumn{1}{c}{{(7)}} &  \multicolumn{1}{c}{{(8)}}\\
                 \midrule

                 Distance from the capital&       1.208***&       1.394   &       1.133** &       1.961***&       1.295** &       0.965   &       1.438** &       1.723*** \\
                 \smallskip
                 &      (0.31)   &      (1.17)   &      (0.52)   &      (0.70)   &      (0.57)   &      (0.63)   &      (0.56)   &      (0.59)   \\
                 Internet coverage  &       1.706*  &       1.271   &       0.397   &       3.374***&       1.439*  &       0.982   &       1.236*  &       2.540***\\
                 \smallskip
                 &      (0.92)   &      (1.32)   &      (0.63)   &      (1.18)   &      (0.74)   &      (0.76)   &      (0.72)   &      (0.87)   \\
                   Distance from the capital $\times$ Internet coverage&      -1.909** &      -2.422   &      -1.785*  &      -3.447*  &      -1.994   &      -1.477   &      -2.577** &      -3.103**  \\
                   \medskip
                   &      (0.83)   &      (2.41)   &      (0.98)   &      (1.81)   &      (1.24)   &      (1.38)   &      (1.28)   &      (1.39)   \\
                 \midrule
                 \smallskip
                Individual \& regional controls  & Yes & Yes & Yes & Yes& Yes & Yes & Yes & Yes\\
                \smallskip
                Country X Round FE       & Yes& Yes & Yes& Yes & Yes& Yes & Yes& Yes\\
                \smallskip
                Observations         &       36,389   &       62,039   &       37,348   &       60,887   &       25,442   &       29,913   &       20,074   &       23,246   \\
                \bottomrule
                \multicolumn{9}{p{24cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
                includes values of: normalized distance from the largest non-capital city, age, age squared, sex,
                education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper news consumption, radio consumption. The set of regional controls includes values of: nighttime light, population density, region area, president birthplace dummy. Education, rural/urban, and age controls are omitted from columns (1-2), (3-4), and (5-8), respectively.*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
                \end{tabular}
                }
                \end{table}

>>>>

\usepackage[dvipsnames]{xcolor}

@@

@@

\usepackage{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{url}
\usepackage{dcolumn}
\usepackage{ctable}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{rotating}
\usepackage{subcaption}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{soul}
\usepackage{float}
\usepackage{bbding} % checkmark symbol
\usepackage{comment} % checkmark symbol

@@

%Bibliography
\usepackage{natbib}

\newtheorem{hyp}{Hypothesis}
\makeatletter
\newcounter{subhyp}
\let\savedc@hyp\c@hyp
\newenvironment{subhyp}
 {%
  \setcounter{subhyp}{0}%
  \stepcounter{hyp}%
  \edef\saved@hyp{\thehyp}% Save the current value of hyp
  \let\c@hyp\c@subhyp     % Now hyp is subhyp
  \renewcommand{\thehyp}{\saved@hyp\alph{hyp}}%
 }
 {}
\newcommand{\normhyp}{%
  \let\c@hyp\savedc@hyp % revert to the old one
  \renewcommand\thehyp{\arabic{hyp}}%
}
\makeatother

@@

%Expectation operator
\newcommand{\Expect}{{\rm I\kern-.3em E}}

@@

\usepackage{titlesec}
\usepackage[dvipsnames]{xcolor}

\titleformat{\section}
{\color{WildStrawberry}\normalfont\LARGE\bfseries}
{\color{WildStrawberry}\thesection}{1em}{}

\titleformat{\subsection}
{\color{ForestGreen}\normalfont\Large\bfseries}
{\color{ForestGreen}\thesubsection}{1em}{}

\titleformat{\subsubsection}
{\color{NavyBlue}\normalfont\large\bfseries}
{\color{NavyBlue}\thesubsubsection}{1em}{}

\titleformat{\paragraph}[runin]
{\normalfont\normalsize\bfseries}
{}{0pt}{}

\titleformat{\subparagraph}[runin]
{\normalfont\normalsize\bfseries}
{}{0pt}{}

% Adjust spacing after headings
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip}
\titlespacing*{\subsection}{0pt}{\baselineskip}{\baselineskip}
\titlespacing*{\subsubsection}{0pt}{\baselineskip}{\baselineskip}
\titlespacing*{\paragraph}{0pt}{\baselineskip}{\baselineskip}
\titlespacing*{\subparagraph}{0pt}{\baselineskip}{\baselineskip}

% Adjust numbering depth
\setcounter{secnumdepth}{3} % Number subsubsections

\usepackage{hyperref}
\usepackage{chngcntr}
\usepackage{lscape}
\usepackage{rotate}
\usepackage{pdflscape}

\usepackage{booktabs}      % For professional table lines
\usepackage{multirow}      % For merged cells across rows
\usepackage{makecell}      % For better cell formatting
\usepackage{array}         % For advanced array and table formatting
\usepackage{colortbl}      % If you want to use colored cells

@@

\title{The Death of Distance: Mobile Internet
and Political Trust in Africa \\  \vspace{0.75cm} \underline{Tables}}

@@

@@

\begin{table}[H]
    \sffamily
    \caption{{Effect of distance from the capital on political trust}}
    \centering
    %\footnotesize
    \resizebox{8cm}{!}{
    \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
    \\
    \toprule
    \toprule
    &  \multicolumn{4}{c}{{OLS}}  \\
    \cmidrule(r){2-5}
    &  \multicolumn{4}{c}{{Political trust}}  \\
    \cmidrule(r){2-5}
    & \multicolumn{2}{c}{{Base sample}} & \multicolumn{2}{c}{{Border sample}}\\
        \cmidrule(r){2-3}
        \cmidrule(r){4-5}
        & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
     \midrule

     Distance from the capital&       0.300***&       0.298***&       0.618***&       0.341** \\
     \smallskip
     &      (0.04)   &      (0.03)   &      (0.15)   &      (0.16)   \\
     \midrule
     \smallskip
    Individual \& regional controls  & Yes & Yes & Yes & Yes  \\
    \smallskip
    Country controls & Yes& No& Yes& No\\
    \smallskip
    Round FE & Yes & No& Yes & No\\
    \smallskip
    Country X Round FE       & No & Yes& No & Yes\\
    \smallskip
    Ethnic homeland FE & No & No & Yes& Yes\\
    \smallskip
    Observations           &      107,117   &      111,570   &       10,790   &       11,924   \\
    Adjusted-R$^2$         &       0.105   &       0.156   &       0.140   &       0.172   \\
                          \bottomrule
    \multicolumn{5}{p{12.5cm}}{\footnotesize \emph{Notes}: The border sample includes individuals residing within a 40-kilometer buffer around a country border that overlaps with a historical ethnic homeland, as defined by Murdock (1959). Robust standard errors clustered at the region x round level  for the base sample and ethnic homeland x region x round level for the border sample are in parentheses. The set of individual controls
    includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
    education, employment status, rural/urban situation, personal economic conditions perception, interest in politics, TV news consumption, radio news consumption, newspaper consumption. (3) and (4) also include a measure of ethnic discrimination. The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy. The set of country controls includes: log(GDP.p.c.), log(area), V-Dem Polyarchy index, World Bank corruption index, political regime type, colonial origin. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
    \end{tabular}
    }
    \end{table}

    \begin{table}[H]
        \sffamily
        \caption{Effect of internet coverage on political trust by distance}
        \centering
        %\footnotesize
        \resizebox{12cm}{!}{
        \begin{tabular}{@{\extracolsep{5pt}} l c c c c c c}
        \\
        \toprule
        \toprule
        & \multicolumn{5}{c}{{Base sample}}\\
        \cmidrule(r){2-6}
        & \multicolumn{1}{c}{{OLS}} & \multicolumn{3}{c}{{First Stage}} & \multicolumn{1}{c}{{2SLS}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-5}
            \cmidrule(r){6-6}
            & \multicolumn{1}{c}{{Political trust}} & \multicolumn{1}{c}{{Internet coverage}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{Distance $\times$ Internet coverage}} & \multicolumn{1}{c}{{Political trust}}\\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            \cmidrule(r){5-5}    
            \cmidrule(r){6-6}    
            & \multicolumn{1}{c}{{(1)}} & \multicolumn{1}{c}{{(2)}} & \multicolumn{1}{c}{{}} &  \multicolumn{1}{c}{{(3)}} & \multicolumn{1}{c}{{(4)}}\\

@@

    Distance from the capital&       0.453***&&&&       1.523***\\
    \smallskip
    &      (0.05)   &&&&      (0.56)   \\
    Internet coverage&      -0.015   &&&&       1.770** \\
\smallskip
&      (0.06)   &&&&      (0.69)   \\
Distance from the capital $\times$ Internet coverage&     -0.466***&&&&       -2.950**         \\
\smallskip
            &      (0.10)   &&&&        (1.45)           \\

   Lightning strikes && -0.002*** && -0.000  \\
    \smallskip&& (0.00) && (0.00) \\
    Distance from the capital city $\times$ Lightning strikes&&-0.000 && -0.001***\\
    \medskip&& (0.00) && (0.00)\\

         \midrule
        SW \emph{F} - Lightning strikes &-&-& 13.74&- &-\\
        \smallskip
        SW \emph{F} - Distance $\times$ Lightning strikes &-&-& 8.62 &-&-\\
        \smallskip
        Individual \& regional controls  & Yes & Yes &&  Yes & Yes\\
        \smallskip
        Country X Round FE       & Yes & Yes&- & Yes & Yes \\
        \smallskip
        Observations       &       111,570    &113,243 & 113,243&       111,570  \\
        Adjusted-R$^2$    &       0.158     &-&-&-&  \\
                              \bottomrule
        \multicolumn{6}{p{25cm}}{\footnotesize \emph{Notes}: % Set font size to 8pt with 10pt line spacing
        \emph{Notes}: Robust standard errors clustered at the region x round level. The set of individual controls
        includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
        education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper consumption, radio consumption. The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
    \end{tabular}}
        \end{table}

        \begin{table}[H]
            \sffamily
            \caption{{Political accountability}}
            \centering
            %\footnotesize
            \resizebox{12cm}{!}{
            \begin{tabular}{@{\extracolsep{5pt}} l c c}
            \\
            \toprule
            \toprule
            & \multicolumn{2}{c}{2SLS}\\
            \cmidrule(r){2-3}
            &\multicolumn{1}{c}{{Vote against ruling party}}&  \multicolumn{1}{c}{{Country performance}}  \\
            \cmidrule(r){2-2}
            \cmidrule(r){3-3}
            & \multicolumn{1}{c}{{Base sample}} & \multicolumn{1}{c}{{Base sample}}\\
                \cmidrule(r){2-2}
                \cmidrule(r){3-3}
                & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}\\
             \midrule

            Distance from the capital&      -0.932***&       1.874***\\
            \smallskip
            &      (0.28)   &      (0.65)   \\
            Internet coverage&       -1.163***&       2.089***\\
            \smallskip
            &        (0.41)   &      (0.77) \\
            Distance from the capital $\times$ Internet coverage&       2.104***&      -4.200** \\
            \medskip
            &      (0.74)   &      (1.69)   \\

             \midrule
             \smallskip
            Individual \& regional controls  & Yes & Yes\\
            \smallskip
            Country X Round FE       & Yes& Yes\\
            \smallskip
            Observations      &      74,959   &      111,696  \\            \bottomrule
            \multicolumn{3}{p{18cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
            includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
            education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper consumption, radio consumption. The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
            \end{tabular}
            }
            \end{table}

            \begin{table}[H]
                \sffamily
                \caption{{Media and institutions freedom}}
                \centering
                %\footnotesize
                \resizebox{10cm}{!}{
                \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
                \\
                \toprule
                \toprule
                & \multicolumn{4}{c}{2SLS: Political trust}\\
                \cmidrule(r){2-5}
                & \multicolumn{4}{c}{{Base sample}}\\
                \cmidrule(r){2-5}
                &\multicolumn{2}{c}{{Media}}&  \multicolumn{2}{c}{{Institutions}}\\
                \cmidrule(r){2-3}
                    \cmidrule(r){4-5}
                    & \multicolumn{1}{c}{{Free}} & \multicolumn{1}{c}{{Captured}}& \multicolumn{1}{c}{{Free}} & \multicolumn{1}{c}{{Captured}}\\
                    \cmidrule(r){2-2}
                    \cmidrule(r){3-3}
                    \cmidrule(r){4-4}
                    \cmidrule(r){5-5}
                    & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
                 \midrule

              Distance from the capital&      -8.382   &       1.083** &       2.367   &       0.938***\\
              \smallskip
              &      (24.71)   &      (0.42)   &      (1.50)   &      (0.32)   \\
              Internet coverage&      -5.260   &       1.004   &       2.653*  &       0.762   \\
              \smallskip
              &      (19.11)   &      (0.74)   &      (1.49)   &      (0.69)   \\
              Distance from the capital $\times$ Internet coverage&      18.335   &      -2.149*  &      -5.132   &      -1.524**  \\
              \medskip
              &       (52.59)   &      (1.25)   &      (3.92)   &      (0.77)   \\

                 \midrule
                 \smallskip
                Individual \& regional controls  & Yes & Yes & Yes & Yes\\
                \smallskip
                Country X Round FE       & Yes& Yes & Yes& Yes\\
                \smallskip
                Observations          &       50,288   &       61,282   &       51,737   &       59,833  \\
                \bottomrule
                \multicolumn{5}{p{15cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
                includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
                education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper consumption, radio consumption. The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy. *** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
                \end{tabular}
                }
                \end{table}

                \begin{table}[H]
                    \sffamily
                    \caption{{Individual heterogeneity}}
                    \centering
                    %\footnotesize
                    \resizebox{10cm}{!}{
                    \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
                    \\
                    \toprule
                    \toprule
                    & \multicolumn{4}{c}{2SLS: Political trust}\\
                    \cmidrule(r){2-5}
                    & \multicolumn{4}{c}{{Base sample}}\\
                    \cmidrule(r){2-5}
                    &\multicolumn{2}{c}{{Education}}&  \multicolumn{2}{c}{{Urban/Rural}}\\
                    \cmidrule(r){2-3}
                        \cmidrule(r){4-5}
                        & \multicolumn{1}{c}{{$<$ Secondary}} & \multicolumn{1}{c}{{$\geq$ Secondary}}& \multicolumn{1}{c}{{Urban}} & \multicolumn{1}{c}{{Rural}}\\
                        \cmidrule(r){2-2}
                        \cmidrule(r){3-3}
                        \cmidrule(r){4-4}
                        \cmidrule(r){5-5}
                        & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
                     \midrule

                       Distance from the capital&        1.467***&       1.440   &       1.074** &       2.666***\\
                       \smallskip
                       &      (0.45)   &      (1.44)   &      (0.54)   &      (0.89)  \\
                       Internet coverage&       1.613** &       1.632   &       0.525   &       4.471***\\
                       \smallskip
                       &     (0.63)   &      (1.34)   &      (0.62)   &      (1.48)    \\
                       Distance from the capital $\times$ Internet coverage&      -2.901** &      -2.688   &      -1.787   &      -5.898** \\
                       \medskip
                       &       (1.24)   &      (3.22)   &      (1.12)   &      (2.55)    \\

                     \midrule
                     \smallskip
                    Individual \& regional controls  & Yes & Yes & Yes & Yes\\
                    \smallskip
                    Country X Round FE       & Yes& Yes & Yes& Yes\\
                    \smallskip
                    Observations         &        79,394   &       32,176   &       42,509   &       69,061\\
                    \bottomrule
                    \multicolumn{5}{p{18cm}}{\footnotesize \emph{Notes}: Robust standard errors clustered at the region x round level are in parentheses. The set of individual controls
                    includes measures of: normalized distance from the largest non-capital city, age, age squared, sex,
                    education, employment status, rural/urban situation, personal economic conditions perception, ethnic discrimination, interest in politics, TV news consumption, newspaper consumption, radio consumption. The set of regional controls includes measures of: nighttime light, population density, region area, president birthplace dummy. Education, rural/urban, and age controls are omitted from columns (1-2), (3-4), and (5-8), respectively.*** / ** / * represent significance at the 0.01 / 0.05 / 0.10 levels, respectively.}
                    \end{tabular}
                    }
                    \end{table}

\newpage

\centering{\large{\textbf{APPENDIX}}}

\begin{table}[H]
  \sffamily
  \caption{{Effect of internet coverage on internet news consumption and internet use}}
  \centering
  %\footnotesize
  \resizebox{8cm}{!}{
  \begin{tabular}{@{\extracolsep{5pt}} l c c c c}
  \\
  \toprule
  \toprule
  &  \multicolumn{4}{c}{{OLS}}  \\
  \cmidrule(r){2-5}
  & \multicolumn{2}{c}{{Internet news}} & \multicolumn{2}{c}{{Internet use}}\\
      \cmidrule(r){2-3}
      \cmidrule(r){4-5}
      & \multicolumn{1}{c}{{(1)}} &  \multicolumn{1}{c}{{(2)}}  & \multicolumn{1}{c}{{(3)}} &  \multicolumn{1}{c}{{(4)}}\\
   \midrule

   Internet coverage &       0.900***&       1.127***&       0.948***&       1.217***\\
   \medskip&      (0.06)   &      (0.05)   &      (0.06)   &      (0.06)   \\
